Multilevel regression models

### 2023-10-19 procesamiento/prod_analysis-full-sample.Rmd
variables

---
title: "Multilevel regression models"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
# summary(giniD_int)

@@

```{r mod-other-macro-ordinal,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  # filter(!country2 %in% c("CHN")) %>%
  # filter(!country2 %in% c("TWN")) %>%
  # filter(!country2 %in% c("JPN")) %>%
  # filter(!country2 %in% c("ZAF")) %>%
  # filter(!country2 %in% c("PHL")) %>%
  # filter(!country2 %in% c("THA")) %>%
  # filter(!country2 %in% c("USA")) %>%
  # filter(!country2 %in% c("GBR")) %>%
  # filter(!country2 %in% c("ISL")) %>%
  # filter(!country2 %in% c("TUR","EST")) %>%
  # filter(!country2 %in% c("MEX")) %>%
# filter(!country2 %in% c("HUN")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
  # filter(PARTLIV %in% c(0,1,2,3)) %>%
  # filter(!region %in% c("Northern America","South America")) %>%
  # filter(Q03pcm!="Missing") %>%
    # filter(oecd=="OECD") %>%
  na.omit()

>>>>

---
title: "Multilevel regression models"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
base <- glmer(formula(main),data=dfreg,weights = WEIGHT,family = "binomial")
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

@@

```{r mod-other-macro-binary,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$redistB <- car::recode(df1$redist,"4:5=1;1:3=0",as.factor = T)
dfreg <- df1 %>% dplyr::select(redist=redistB,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  # filter(!country2 %in% c("CHN")) %>%
  # filter(!country2 %in% c("TWN")) %>%
  # filter(!country2 %in% c("JPN")) %>%
  # filter(!country2 %in% c("ZAF")) %>%
  # filter(!country2 %in% c("PHL")) %>%
  # filter(!country2 %in% c("THA")) %>%
  # filter(!country2 %in% c("USA")) %>%
  # filter(!country2 %in% c("GBR")) %>%
  # filter(!country2 %in% c("ISL")) %>%
  # filter(!country2 %in% c("TUR","EST")) %>%
  # filter(!country2 %in% c("MEX")) %>%
# filter(!country2 %in% c("HUN")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
  # filter(PARTLIV %in% c(0,1,2,3)) %>%
  # filter(!region %in% c("Northern America","South America")) %>%
  # filter(Q03pcm!="Missing") %>%
    # filter(oecd=="OECD") %>%
  na.omit()
